Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-04-12 meta_analysis_sexual_selection_pop_fitness.Rmd
12/4/18 update

# define upper and lower bounds
prelim.data$lowerci <- prelim.data$g - 1.96*(sqrt(prelim.data$var.g))
prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))

# Get author and year in one
short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
                                 short = prelim.data$Authors %>% unique() %>% 
  as.character() %>% 
  strsplit(split = ",") %>% 
  sapply(FUN=function(x) x[1])) %>%
  left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
  mutate(suffix = "")

# Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
dups <- with(short.author.names, table(short, Year)) %>% melt()
dups <- dups[dups$value > 1, ]
for(i in 1:nrow(dups)){
  short.author.names$suffix[
    short.author.names$short == dups$short[i] &
      short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
}

# Add the AuthorYear column to the dataframe of effect sizes
short.author.names <- short.author.names %>%
  mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
  select(long, AuthorYear)
prelim.data <- prelim.data %>% 
  left_join(short.author.names, by = c("Authors" = "long"))

@@

>>>>

# define upper and lower bounds
prelim.data$lowerci <- prelim.data$g - 1.96*(sqrt(prelim.data$var.g))
prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))
# 
# # Get author and year in one
# short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
#                                  short = prelim.data$Authors %>% unique() %>% 
#   as.character() %>% 
#   strsplit(split = ",") %>% 
#   sapply(FUN=function(x) x[1])) %>%
#   left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
#   mutate(suffix = "")
# 
# # Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
# dups <- with(short.author.names, table(short, Year)) %>% melt()
# dups <- dups[dups$value > 1, ]
# for(i in 1:nrow(dups)){
#   short.author.names$suffix[
#     short.author.names$short == dups$short[i] &
#       short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
# }
# 
# # Add the AuthorYear column to the dataframe of effect sizes
# short.author.names <- short.author.names %>%
#   mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
#   select(long, AuthorYear)
# prelim.data <- prelim.data %>% 
#   left_join(short.author.names, by = c("Authors" = "long"))

@@

Or we could run the models as subsets (one for each outcome)

```{r}
outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
outcome.models <-  llply(outcome.list, function(x) rma(g, var.g, 
                          mods = ~ 1, 
                          method = "REML",
                          subset = (Outcome_f == x),
                          data = prelim.data))

df.list <- as.data.frame(do.call("rbind", outcome.models)) # data frame of model results

simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "I2"))
outcome.frame <- format(simple.frame, digits = 2)
outcome.frame <- add_rownames(outcome.frame, "Outcome")
outcome.frame$b <- as.numeric(outcome.frame$b)
outcome.frame$ci.lb <- as.numeric(outcome.frame$ci.lb)
outcome.frame$ci.ub <- as.numeric(outcome.frame$ci.ub)
outcome.frame %>% pander
```

Check the results on a plot
```{r}
outcome.frame %>% ggplot(aes(x = b, y=Outcome)) + 
  geom_vline(xintercept = 0, linetype = 2, colour = "grey70") + 
  geom_errorbarh(aes(xmin = ci.lb, 
                     xmax = ci.ub), height = 0, position = pd, show.legend = F) +
  geom_point(position = pd, size=3, shape=21, color = "grey20") + 
  ylab("Outcome\n")+
  xlab("\nEffect Size (Hedges g)")+
  xlim(-2.5, 2.5)+
  ggtitle('Effects of Sex and Stress \non Population Fitness')
```
